### 2016-03-10 paper/layered_depthmap.tex
yasu

\mysubsubsection{Baseline methods}
The number of labels is extremely large (an order of 10,000 \yasu{what
were the number of labels in our cvpr16?}), which eliminates the
possibility of using hierarchical fusion. Therefore, we will evaluate
fusion move and parallel fusion move algorithm as in the case of optical
flow problem, where one solution proposal repeats being fused via QPBO.

\mysubsubsection{Swarm fusion implementation}
All the three swarm fusion methods are tested.

>>>>

\mysubsubsection{Competing methods}
The number of labels is extremely large (an order of 10,000 \yasu{what
were the number of labels in our cvpr16?}), which eliminates the
possibility of using hierarchical fusion. Therefore, we will evaluate
fusion move and parallel fusion move algorithm as in the case of optical
flow problem, where one solution proposal repeats being fused via QPBO.

\mysubsubsection{Swarm fusion architecture}
All the three swarm fusion methods are tested.

### 2016-03-10 paper/stereo.tex
yasu

% We pick three representative problems in Computer Vision to evaluate the
% effectiveness of the Fusion swarm methods against existing methods. We
% control the SF architectures for each problem independently to make
% compa
%
%\yasu{this section is very rough at the moment. requires polishing. but
%algorithms might change as we run experiments.}  We now explain detailed
%implementation of the Swarm Fusion method for three problems in Computer
%Vision (See Fig.~\ref{fig:problem}).  5
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
 compare our Swarm Fusion methods against various baselines on a
 depthmap stereo~\cite{middle_bury_stereo}, an optical
 flow~\cite{middlebury_optical_flow}, or a layered depthmap
 estimation~\cite{layered_depthmap} problem.  }\label{fig:problem}
\end{figure}

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
submodular pairwise terms. Unary terms are computed as the average
Normalized Cross Correlation score between the reference image and the
others inside a $7\times 7$ pixels window. Pairwise terms are simple
Pottz model. The total energy is defined by the sum of the two, while
the pairwise term is scaled by a factor of \yasu{X value}.
%
We use Middlebury stereo datasets for the experiments.

\mysubsubsection{Baseline methods}

\noindent
Parallel alpha-expansion~\cite{delong} or hierarchical
fusion~\cite{delong,olga} with Graph-cuts (when submodular) or QPBO
(when non-submodular) have been the most effective parallel techniques.
%

\mysubsubsection{Swarm fusion implementation}

\noindent
To make the comparison simple, we restrict our proposal generation to be
constant-label proposals, and limit to binary fusion so that Swarm
Fusion will also use either Graph-cuts or QPBO for the core
optimization. Limiting to binary fusion deprived SF of multi-way fusion
and SF architecture becomes the middle example in the bottom row of
Fig.~\ref{fig:model}.
%
The advantage of SF is that threads exchange solutions throughout the
process.

>>>>

% We pick three representative problems in Computer Vision to evaluate the
% effectiveness of the Fusion swarm methods against existing methods. We
% control the SF architectures for each problem independently to make
% compa
%
%\yasu{this section is very rough at the moment. requires polishing. but
%algorithms might change as we run experiments.}  We now explain detailed
%implementation of the Swarm Fusion method for three problems in Computer
%Vision (See Fig.~\ref{fig:problem}).  5
\begin{figure}[tb]
 \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
 compare our Swarm Fusion methods against competing approaches on a
 depthmap stereo~\cite{middle_bury_stereo}, an optical
 flow~\cite{middlebury_optical_flow}, or a layered depthmap
 estimation~\cite{layered_depthmap} problem. In the layered depthmap
 problem, the input is an RGBD image, and the output is multiple layeres
 of depthmaps. Each layer is a piecewise smooth parametric surface
 model.}\label{fig:problem}
\end{figure}

\subsection{Swarm Fusion stereo}
We start with a simple depthmap stereo problem with standard unary and
pairwise terms. We employ submodular pairwise terms to make this stereo
represent relatively ``easy'' MRF inference problems.
%
Unary terms are computed as the average Normalized Cross Correlation
score between the reference image and the others inside a $7\times 7$
pixels window. Pairwise terms are simple Pottz model. The total energy
is defined by the sum of the two, while scaling the pairwise term by a
factor of \yasu{X value}.
%
We use Middlebury stereo datasets for the experiments.

\mysubsubsection{Competing methods}

\noindent The sophistication of photometric consistency
function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
stereo problems.  Our experiments have also supported this, where the
fusion method (i.e., the use of proposal generation) rather makes it slow
due to the overhead.  Therefore, we pick parallel
alpha-expansion~\cite{delong} and hierarchical fusion~\cite{delong,olga}
with graph-cuts optimization as the competing methods.

\mysubsubsection{Swarm fusion architecture}

\noindent To make the comparison simple, we restrict our proposal
generation to be constant-label proposals, and limit to binary fusion
(i.e., without multi-way fusion). Graph-cuts is used in fusing a
constant-label proposal as the energy is submodular. QPBO is used in
fusing a different solution from another thread as the energy is
non-submodular.  Due to the lack of multi-way fusion, the swarm fusion
architecture for the stereo problem is represented by the middle
example at the bottom of Fig.~\ref{fig:model}.
